\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-04-24 doc/paper.tex
More tinkering mostly for readability.  Mentioned sarah as the competitor.

These motivate both exploring non-minimal SUSY models which ameliorate
the naturalness problems introduced, by, for example, raising the tree
level Higgs mass, and models developed with a fresh perspective,
  based on other considerations.  In both cases exploration of such
  models can be aided if it is possible to quickly create a fast
  spectrum generator.

\fs is designed for precisely this task. \fs is a MATHEMATICA package
which with the help of \sarah
\cite{Staub:2010ty,Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta}
creates a fast, modular C++ spectrum generator for a user specified
SUSY model.  The generated code structure is designed to be as
flexible as possible to accommodate different types of extensions and
due to it's modular nature it is easy to modify, add new features to
or combine with other programs.  The generated code has been
extensively tested against well known spectrum generators and as well
providing a solution for new SUSY models the generated MSSM and NMSSM
codes offer a modern and fast alternative to the existing public
spectrum generators.

>>>>

These motivate both exploring non-minimal SUSY models which ameliorate
the naturalness problems by, for example, raising the tree level Higgs
mass, and models developed with a fresh perspective, based on other
considerations.  In both cases exploration of such models can be aided
if it is possible to quickly create a fast spectrum generator.
Currently there is only option for this, a SPheno-like FORTRAN code
which can be generated from
\sarah\cite{Staub:2010ty,Staub:2009bi,Staub:2010jh,Staub:2012pb,Staub:2013tta}.

\fs provides a much needed alternative to this with a structure which
has been freshly designed to accommodate as general range of models as
possible and to be easily adaptable to changing goals and new
ideas. \fs is a MATHEMATICA package which uses \sarah to create a
fast, modular C++ spectrum generator for a user specified SUSY model.
The generated code structure is designed to be as flexible as possible
to accommodate different types of extensions and due to it's modular
nature it is easy to modify, add new features and combine with other
programs.  The generated code has been extensively tested against well
known spectrum generators and as well providing a solution for new
SUSY models the generated MSSM and NMSSM codes offer a modern and fast
alternative to the existing public spectrum generators.
